The Globular Cluster System of the Auriga Simulations

### 2019-05-14 AurigaGCS.tex
Updated figures for 4.3

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted $R_{\text{GC}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.19 \% of the total MW GCS mass in the Harris catalog.
        \emph{Bottom}: Same for M31, showing 366 GCs and 88.38 \% of the total
        mass in CR16 \citep[data from][]{2016ApJ...824...42C}. Note that the
        range of the colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS 
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
radial distribution of star particles in all Auriga L4 simulations. We notice 
that the old insitu populations are much more centrally distributed, whereas
the old accreted component has a larger radial extent. Moreover, the dispersion
increases with increasing mean value of the radial distribution as may be expected
for a quantity that cannot have negative values.

@@

We investigate whether the Auriga simulations still produce sufficient mass when 
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{GC}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to 
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total 
mass in the MW (M31) GCS to obtain the median mass excess produced by the star 
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc} for mass excess with respect to the MW (M31) GCS.

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_iold_36bins_mean}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all Auriga haloes
        (level 3, 4 and 5). Here we consider the old ($>$~10~Gyr) stars in all
        simulations and color-code the \textbf{mean value} (of 40 Auriga haloes)
        \label{fig:Au-FeHRgc}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_MW_iold_36bins_mean}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au-all_RgcFeH_HistogramMassWeighted_M31_iold_36bins_mean}.png}
    \caption{
        Caption
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
    \caption{Same as Figure~\ref{fig:FeH}, but here the colours indicate resolution
        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three
        haloes we find marginal increases in the mass normalization with increasing
        resolution level.
        \label{fig:logMFeH_res}
    }

\end{figure*}
\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
    \caption{Same as Figure~\ref{fig:Rgc}, but here the colours indicate resolution
        level: L3 green, L4 orange, and L5 blue. \emph{Left:} Auriga halo 6.
        \emph{Mid:} Auriga halo 16. \emph{Right:} Auriga halo 24. For all three
        haloes we find marginal increases in the mass normalization with increasing
        resolution level.
        \label{fig:logMRgc_res}
    }

>>>>

\begin{figure}
    \includegraphics[width=\columnwidth]
        {{MW_RgcFeH_HistogramMassWeighted_Harris1996ed2010data}.png}
    \includegraphics[width=\columnwidth]
        {{M31_RgcFeH_HistogramMassWeighted_CaldwellRomanowsky2016data}.png}
    \caption{
        \emph{Top}: Mass-weighted $R_{\text{GC}}$-[Fe/H] distribution of
        151 GCs in the MW \citep[data from][2010 ed.]{1996AJ....112.1487H}, which
        is 98.6 (92.2) \% of the total mass (clusters) of the MW GCS in the Harris 
        catalog. \emph{Bottom}: Same for M31, showing 366 GCs and 88.4 (83.9) \% 
        of the total mass (clusters) in CR16 \citep[data from][]{2016ApJ...824...42C}. 
        Note that the range of the colourmap differs in both figures.
        \label{fig:observations_FeHRgc}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\columnwidth]{{Rgc_mu_sigma-trim}.png}
    \caption{
        Mean and standard deviation of the radial distribution of star particles
        in each of the thirty Auriga L4 haloes compared to the MW (M31) GCS 
        shown in purple (magenta).
        \label{fig:Rgc_mu_sigma}
    }
\end{figure}
Figure~\ref{fig:Rgc_mu_sigma} shows the mean and standard deviation of the
radial distribution of star particles in all Auriga L4 simulations. We notice 
that the old insitu populations are much more centrally distributed, whereas
the old accreted component has a larger radial extent. Moreover, the dispersion
increases with increasing mean value of the radial distribution as may be expected
for a non-negative quantity.

@@

We investigate whether the Auriga simulations still produce sufficient mass when 
the GC candidates are two-dimensionally binned in [Fe/H] and $R_\text{GC}$. First
we sum the total simulated mass in each bin (for an individual Auriga simulation),
then we calculate the median over all thirty Auriga L4 haloes (in each bin, see
Figure~\ref{fig:Au-FeHRgc} which can be compared to 
Figure~\ref{fig:observations_FeHRgc}). Finally, we divide these value by the total 
mass in the MW (M31) GCS to obtain the median mass excess produced by the star 
formation model implemented in the Auriga simulations. See the top (bottom) panel
of Figure~\ref{fig:Au-FeHRgc-ratio} for mass excess with respect to the MW (M31) GCS.

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_iold-trim}.png}
    \caption{
        Mass-weighted [Fe/H]-$R_{\text{GC}}$ distribution of all thirty Auriga 
        L4 haloes. Here we consider only the GC candidates (age $>$~10~Gyr) stars
        in and color-code by the \textbf{median} (values also shown in each bin). 
        The numbers in parenthesis show how many star particles fall within the
        bin. Note that the range of the colourmap again differs (for improved
        contrast within the plot).
        \label{fig:Au-FeHRgc}
    }
\end{figure}

\begin{figure}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_MW_iold-trim}.png}
    \includegraphics[width=0.49\textwidth]
        {{Au4-median_RgcFeH_HistogramMassWeighted_M31_iold-trim}.png}
    \caption{
        The top (bottom) panel shows the logarithm of the ratio of simulated mass
        to mass in the MW (M31) GCS, i.e. the logarithm of the mass excess. The 
        color-coded values are also shown in each bin. Note that the three bins 
        in the upper right corner are left blank because the observations have
        zero mass there, and that the numbers indicate how much (median) mass is 
        produced by the simulations in those bins.
        \label{fig:Au-FeHRgc-ratio}
    }
\end{figure}

@@

\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMFeH_Au24}.png}
    \caption{Similar to Figure~\ref{fig:FeH}, but showing one individual Auriga
        halo, where colours indicate the resolution level: L3 green, L4 orange, 
        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16.
        \emph{Right:} Auriga halo 24. For all three haloes we find marginal 
        increases in the mass normalization with increasing resolution level.
        \label{fig:logMFeH_res}
    }

\end{figure*}
\begin{figure*}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au6}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au16}.png}
    \includegraphics[width=0.31\textwidth]{{logMRgc_Au24}.png}
    \caption{Similar to Figure~\ref{fig:Rgc}, but showing one individual Auriga 
        halo, where colours indicate the resolution level: L3 green, L4 orange, 
        and L5 blue. \emph{Left:} Auriga halo 6. \emph{Mid:} Auriga halo 16. 
        \emph{Right:} Auriga halo 24. For all three haloes we find marginal 
        increases in the mass normalization with increasing resolution level.
        \label{fig:logMRgc_res}
    }
